---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BlackjackR
### Written by Aoife Steenson, Jack Wiersma and Louis Thomas

<!-- badges: start -->
<!-- badges: end -->

## Description

__BlackjackR__ Simulates a game of blackjack through the console to allow for user input. The game is simulated by creating a deck of shuffled cards and drawing cards for both the player and the dealer. The player can then use the console to Hit or Stick, based on their choice the player will either receive another card (and given the choice to Hit or Stick again, and so on) or be given the outcome of the game. 6 functions are provided in the package.

  1. `blackjack()`: Emulates a game of blackjack in the console. The game can be simulated or can take in user input. 
  
  2. `count_values()`: sums up the value of all cards in the list passed in
  
  3. `create_card()`: allows the user to create a specific card, can also be used to generate a random card if the user provides no specific input
  
  4. `create_deck()`: creates however many decks of cards specified by the user (default is 1 deck). Each deck is a standard playing deck, 13 cards in each suit, no duplicate cards.
  
  5. `draw_card()`: draws card at the specified index from the specified deck.
  
  6. `print.card()`: extension of the generic print function for the card class. Cards are printed using ASCII art to replicate the look of real playing cards.

## Installation

You can install the development version of BlackjackR from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("AoifeSteenson/BlackjackR")
```

## Example

This is a basic example which shows you how to run a simulated game of blackjack

```{r example}
library(BlackjackR)

blackjack(sim = TRUE)
```


Another example showing how to create a card

```{r}
create_card(9, "heart")
```


A more thorough introduction with more examples and use cases for the methods is provided in the `BlackjackR` vignette.


