---
title: "BlackjackR"
author: "Jack Wiersma, Aoife Steenson, Louis Thomas"
date: " `r Sys.Date() `"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{BlackjackR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(BlackjackR)
```

## Introduction
BlackjackR is an R package which simulates a game of blackjack. In this package, a deck may be created, drawn, and printed. A game of blackjack may also be simulated. In addition, a value count can be done where all of the elements in a card class can be summed.   


## How to install BlackjackR
```{r, eval = FALSE}
install.packages("BlackjackR")
devtools::install_github('AoifeSteenson/BlackjackR')
```

After installation, the library must be loaded: 
```{r, eval = FALSE}
library(BlackjackR)
```

The functions in BlackjackR include blackjack, create_deck, draw_card, print.card, and count values. 


create_deck creates a deck of 52 cards that are in a random order. More than one deck may be created by changing the number n is equal to. 
```{r, eval = FALSE}
x <- create_deck(n = 1)
```


draw_card takes the deck and selects the card at the top of the list. 
```{r, eval = FALSE}
draw_card(card_index = 1, shuffled_deck = x)
```


print_card takes the card that was drawn and prints a picture of the card, or can any card can be selected to print.  
```{r, eval = FALSE}
print.card(object = x)
```

count_values sums all of the values of the elements in a card class
```{r, eval = FALSE}
count_values(x)
```


blackjack() allows the user to simulate a game of blackjack
```{r}
blackjack()
```
```{r}

```

