---
title: "BlackjackR"
author: "Jack Wiersma, Aoife Steenson, Louis Thomas"
date: " `r Sys.Date() `"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{BlackjackR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(BlackjackR)
```

## Introduction
BlackjackR is an R package which simulates a game of blackjack. In this package, a deck may be created, drawn, and printed. A game of blackjack may also be simulated. In addition, a value count can be done where all of the elements in a card class can be summed.   


## How to install BlackjackR
```{r, eval = FALSE}
install.packages("BlackjackR")
devtools::install_github('AoifeSteenson/BlackjackR')
```

After installation, the library must be loaded: 
```{r, eval= FALSE}
library(BlackjackR)
```

The functions in BlackjackR include blackjack, create_deck, draw_card, print.card, and count values. 

## blackjack()
This function allows the user to simulate a game of blackjack
```{r}
blackjack()
```

## count_values()
This function sums all of the values of the elements in a card class
```{r, eval = FALSE}
shuffled_deck <- create_deck()
cards <- list(draw_card(), draw_card())
count_values(cards)
```

## create_deck() 
This function creates a deck of 52 cards that are in a random order. More than one deck may be created by changing the number n is equal to. 
```{r, eval = FALSE}
shuffled_deck <- sample(create_deck())
```


## draw_card() 
This function takes a card from the shuffled deck 
```{r, eval = FALSE}
shuffled_deck <- sample(create_deck())
card_index <- 23
draw_card(23, shuffled_deck)
```


## print_card() 
This function prints a picture of any card in the deck 
```{r, eval = FALSE}
deck <- create_deck()
print(deck[[6]])
print(deck[[13]])
```

